Clustering of Last.fm Music

### 2015-05-04 MSDgroupwriteup.tex
new files

% \documentclass[12pt]{emulateapj}
 \documentclass[12pt,preprint]{aastex}
\usepackage[margin= 1.0in]{geometry}    % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper} % or letter or a5paper or ... etc
\usepackage{float}
\usepackage{amssymb,amsmath}
\usepackage[]{epsfig,graphicx}
\usepackage{color}
\usepackage{verbatim}
\DeclareGraphicsRule{.tif}{png}{.jpg}{`convert Num1 `dirname Num1`/`basename Num1 .tif`.jpg}
\newcommand{\units}[1]{\ensuremath{\, \mathrm{#1}}}
\usepackage{enumitem}
\usepackage{natbib,twoopt}
\newcommand{\degree}{\ensuremath{^\circ}}
\citestyle{apj}
\bibliographystyle{aa}
\usepackage[maxfloats=25]{morefloats}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\usepackage{ amssymb }

\begin{document}
\title{Clustering of Last.fm Music Artists}

@@

We then constructed training and testing matrices, of which both have $N_1$ users (rows denoted by $u_i$) and $N_2$ songs (columns denoted by $v_j$). Of course the matrices will be very sparse, containing zeros in all entries except for those in which a user (rows of matrix) has listened to a song (columns of matrix). The goal is to factor the training matrix into the product of two matrixes, $U$ and $V$. The matrix $U$ will be $N_1 \times d$ and the matrix $V$ will be $d \times N_2$. We want to learn a low-rank factorization (i.e. we choose $d$) so as to restrict the patterns we see in the rows and columns of our original matrix (e.g. we think a priori that if a user likes 1 top 100 song, the user may also like other top 100 songs). There is subjectivity in picking $d$ but $20$ is a common place to start. In the factorized matrices, the predicted rating will be $\hat{M}_{ij} = u_i^T v_j$

@@

\begin{equation}
u_i = \left( \lambda\sigma^2 I + \sum_{j \in \Omega_{w_i}} v_j v_j^T \right)^{-1}\left(\sum_{j \in \Omega_{w_i}} M_{ij} v_{j} \right)
\label{eq1}
\end{equation}

\begin{equation}
v_j = \left( \lambda\sigma^2 I + \sum_{i \in \Omega_{v_j}} u_i u_i^T \right)^{-1}\left(\sum_{j \in \Omega_{v_j}} M_{ij} u_{i} \right)
\label{eq2}
\end{equation}

\begin{equation}
\mathcal{L} = \sum_{(i,j) \in \Omega} \frac{1}{2\sigma^2} {|| M_{ij} - u_i^T v_j||}^2 - \sum_{i=1}^{N_1} \frac{\lambda}{2} ||u_i^2 || - \sum_{i=1}^{N_2} \frac{\lambda}{2} ||v_j^2 || + \text{constant}
\label{eq3} 
\end{equation}

Note: We use a rank 20 matrix for factorization purposes, a $\lambda = 10$, and calculate the variance of the observations for our $\sigma^2$. Also, $\Omega$ is the set of all indices in the matrix which have an observation.

@@

>>>>

% \documentclass[12pt]{emulateapj}
 \documentclass[12pt,preprint]{aastex}
\usepackage[margin= 1.0in]{geometry}    % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper} % or letter or a5paper or ... etc
\usepackage{float}
\usepackage{amssymb,amsmath}
\usepackage[]{epsfig,graphicx}
\usepackage{color}
\usepackage{verbatim}
\DeclareGraphicsRule{.tif}{png}{.jpg}{`convert Num1 `dirname Num1`/`basename Num1 .tif`.jpg}
\newcommand{\units}[1]{\ensuremath{\, \mathrm{#1}}}
\usepackage{enumitem}
\usepackage{natbib,twoopt}
\newcommand{\degree}{\ensuremath{^\circ}}
\citestyle{apj}
\bibliographystyle{aa}
\usepackage[maxfloats=25]{morefloats}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\usepackage{ amssymb }
\newcommand{\TRANSPOSE}{\ensuremath{T}}

\begin{document}
\title{Clustering of Last.fm Music}

@@

We then constructed training and testing matrices, of which both have $N_1$ users (rows denoted by $u_i$) and $N_2$ songs (columns denoted by $v_j$). Of course the matrices will be very sparse, containing zeros in all entries except for those in which a user (rows of matrix) has listened to a song (columns of matrix). The goal is to factor the training matrix into the product of two matrixes, $U$ and $V$. The matrix $U$ will be $N_1 \times d$ and the matrix $V$ will be $d \times N_2$. We want to learn a low-rank factorization (i.e. we choose $d$) so as to restrict the patterns we see in the rows and columns of our original matrix (e.g. we think a priori that if a user likes 1 top 100 song, the user may also like other top 100 songs). There is subjectivity in picking $d$ but $20$ is a common place to start. In the factorized matrices, the predicted rating will be $\hat{M}_{ij} = u_i^\TRANSPOSE  v_j$

@@

\begin{equation}
u_i = \left( \lambda\sigma^2 I + \sum_{j \in \Omega_{u_i}} v_j v_j^\TRANSPOSE \right)^{-1}\left(\sum_{j \in \Omega_{u_i}} M_{ij} v_{j} \right)
\label{eq1}
\end{equation}

\begin{equation}
v_j = \left( \lambda\sigma^2 I + \sum_{i \in \Omega_{v_j}} u_i u_i^\TRANSPOSE  \right)^{-1}\left(\sum_{j \in \Omega_{v_j}} M_{ij} u_{i} \right)
\label{eq2}
\end{equation}

\begin{equation}
\mathcal{L} = \sum_{(i,j) \in \Omega} \frac{1}{2\sigma^2} {|| M_{ij} - u_i^\TRANSPOSE  v_j||}^2 - \sum_{i=1}^{N_1} \frac{\lambda}{2} ||u_i^2 || - \sum_{i=1}^{N_2} \frac{\lambda}{2} ||v_j^2 || + \text{constant}
\label{eq3} 
\end{equation}

\emph{Note}: We use a rank 20 matrix for factorization purposes, a $\lambda = 10$, and calculate the variance of the observations for our $\sigma^2$. Also, $\Omega$ is the set of all indices in the matrix which have an observation.

@@

\begin{figure}[ht]
\begin{minipage}[b]{0.45\linewidth}
\centering
\includegraphics[width=\textwidth]{h845BuzFO9CNgAAAABJRU5ErkJggg==.png}
\caption{default}
\label{fig:figure1}
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[b]{0.45\linewidth}
\centering
\includegraphics[width=\textwidth]{C9LAAAAABJRU5ErkJggg==.png}
\caption{default}
\label{fig:figure2}
\end{minipage}
\end{figure}
